---
title: "Loan_EDLD653_Lab1"
author: "Christopher Loan"
date: "3/30/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
set.seed(123) # Set random number generation
 
m <- lm(mpg ~ 
          hp + cyl + drat, 
        mtcars
        )

l <- list(a = list(m = matrix(1:12, ncol = 3),
              	   v = 1:7),
          b = data.frame(student = 1:15,
                         score = rnorm(15, 100, 10)))
```

# 1. From Model Results

## Extract Tolerance

```{r}
qr_tolerance <- m$qr$tol
qr_tolerance
```
## Extract Term Labels

```{r}
term_labels <- attr(m$terms, "term.labels")
term_labels
```

# 2. From the List

## Two methods to extract `m`

```{r}
m_method_1 <- l$a$m
m_method_1
m_method_2 <- l[['a']][['m']]
m_method_2
```

## Extract Third Column

```{r}
third_col <- l[['a']][['m']][,3]
third_col
```

## Extract Score for 7th Student

```{r}
student_7 <- l[['a']][['m']][7]
student_7
```

# Loops 

# 3. Load `airquality` dataset

## Load 

```{r}
data('airquality')
head(airquality)
```

## Split it by Month

```{r}
split_dat <- split(airquality, airquality$Month)
split_dat
```

# 4. Use a for loop to calculate the mean Ozone by month (remember to remove missing data from the calculation)

```{r}
means <- rep(NA, length(split_dat))
for (i in seq_along(split_dat)){
  means[i] <- mean(split_dat[[i]]$Ozone, na.rm = T)
  
}
means
```

# 5. Replicate this calculation with lapply, sapply, and vapply

```{r}
means_lapply <- lapply(split_dat, function(x) mean(x$Ozone, na.rm = T))
means_lapply
```

# 6. Produce separate plots showing the relation between Ozone and Solar.R for each month (with a single loop).

```{r}
plots <- 
  lapply(split_dat, function(x){
    ggplot(x, aes(Ozone, Solar.R)) +
      geom_point() + 
      geom_smooth()
})
```

```{r}
#dir.create(here::here("plots"))
filenames <- here::here("plots", 
                        paste0('month', 
                               names(split_dat), ".png"))
filenames
```

```{r}
for (i in seq_along(plots)){
  ggsave(filename = filenames[i],
         plots[[i]],
         device = 'png',
         width = 6.5, 
         height = 8)
}
```

